\section{Introduction}

% an introduction to the premise
Ice has long been an object of interest for scientists.
Its unique properties, particularly its lower density than its liquid phase counterpart, are perplexing.
Since the study of ice began in earnest in the early 20th century, more than twenty distinct 
crystal phases have been discovered.
Many methods have been employed in unravelling ice's mysteries, but in recent years Molecular Dynamics (MD)
simulations have become increasingly popular.
MD simulations allow researchers to probe the properties of substances in a range of conditions without 
setting up expensive experiments.
This makes MD simulations uniquely suited to investigate extreme conditions such as high pressure and 
high temperature environments.
In classical MD (the most common form), intermolecular interactions are modelled by 'force fields' which
are functions describing molecular potential energies.
Since MD is a particularly computationally intensive endeavour, early implementations were 'fixed charge
models' whose molecules exhibited no distortion of their charge distribution due to neighbouring atoms.
In the intervening years, however, computational resources have improved and more complex models have been
implemented.
Advances in modelling water have been made primarily by the introduction of 'polarizable' force fields: 
molecules whose charges are affected by the behaviour of their neighbours.
The modern model used in these simulations is the AMOEBA (Atomic Multipole Optimized Energetics for Biomolecular 
Simulation) force field which has been shown to be superior to certain models (TIP3P, ..., ...) in water, steam,
and low pressure ice.
However, AMOEBA is untested for high pressure ice (\textgreater1GPa regime).
An accurate model for ice at these conditions would be able to provide valuable insight into its behaviour and
properties.
In order to assess its suitability, AMOEBA ice will be simulated around the Ice--VIII/Ice--VII phase boundary
in the 2--3GPa region.
Following this, AMOEBA Ice--VII will be heated at very high pressures ($\sim$ 8GPa) to investigate the possibility 
of a new high temperature phase of ice: Ice--VIIp.
The results will then be compared to some common MD water models and experiment.

\subsection{The Crystalline Structure of Ice}
There are many different phases of ice, spanning a wide range of conditions.
The structure of these phases is well-known by diffraction studies.
This variation should be compared to other molecules.
Similar ones (as known by chemists) are \textit{e.g.} $\text{SH}_2$.
The most common phase on Earth is hexagonal Ice--$1_h$.
This is the type of ice which one would find in an ice-cube tray.
It has certain properties which I will talk about briefly.
The polymorphism of the ice crystal is due to the flexibility of its hydrogen-bond network.
There is certainly more to be said about this.
The ices of interest in this examination of AMOEBA are differentiated by their proton
arrangements: ordered (Ice--VIII) and disordered (Ice--VIII).
Their crystal structures are described here.
Ice--VII exhibits a bcc (base-centred cubic) lattice with oxygens at something and the hydrogens 
elsewhere.
Its proton disordering produces ferroelectric effects (or ferromagnetic).
Ice--VIII exhibits an orthorhombic lattice.
Its proton ordering ensures that there is no net electric dipole moment.
It is interesting how these phases are paired across a straight-line phase boundary but exhibit
such different properties.

\subsubsection{Ice Rules}
The crystalline arrangement of water molecules in ice is governed by a set of rules first proposed 
by Bernal and Fowler in their very important paper, Theory of Water and Ionic Solution \cite{bernal1933}:\\
(Direct quote here)\\
Every molecule is surrounded by four others in a tetrahedron and this arrangement will have least energy if the
H-nuclei, which subtend and angle of about $109\deg$ at the centre of the molecule, lie opposite two of the
neighbours, while one of the H-nuclei of each of the remaining neighbours lies opposite a negative corner of the 
original molecule.
These rules have formed the basis of much of the study into ice over the decades.
Consider Pauling's (1933) calculation the entropy of `normal ice' (I$_{h}$) modelled by hexagonal rings as shown in 
Figure \ref{fig:ice-ring}.

% 
%        ice-ring figure
% 

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[scale=1.5]
        \tikzset{
            O/.style={
                circle,
                draw=black,
                fill=red,
                minimum size=10mm,
                line width=1.2pt,
                inner sep=0
            }, H/.style={
                circle,
                draw=black,
                fill=white,
                minimum size=5mm,
                line width=1.2pt,
                inner sep=0
            }, covalent/.style={
                line width=1.4pt,
            }, hbond/.style={
                line width=1.2pt,
                dash pattern=on 1.5pt off 1.5pt
            },
        }

        \def\r{2}
        \def\shift{6} % horizontal separation
        
        % ==== ring 1 ====
        \foreach \i in {1,...,6} {
            \node[O] (O\i) at ({90 + (\i-1)*60}:\r) {};
        }

        \foreach \i [evaluate=\i as \j using {int(mod(\i,6)+1)}] in {1,...,6} {
            \path (O\i.center) -- (O\j.center) coordinate[pos=0.40] (Hpos);
            \node[H] (H\i) at (Hpos) {};

            \draw[covalent] (O\i) -- (H\i); % solid bond

            \draw[hbond] (H\i) -- (O\j); % dashed bond
        }
        
        % ==== ring 2 ====
        \foreach \i in {1,...,6}{
            \node[O] (O2\i) at ({\shift + \r*cos(90+(\i-1)*60)}, {\r*sin(90+(\i-1)*60)}) {};
        }

        \foreach \i [evaluate=\i as \j using {int(mod(\i,6)+1)}] in {1,...,6}{
            \path (O2\i.center) -- (O2\j.center) coordinate[pos=0.60] (Hpos2); % flipped
            \node[H] (H2\i) at (Hpos2) {};
            \draw[hbond] (O2\i) -- (H2\i);
            \draw[covalent] (H2\i) -- (O2\j);
        }

        \draw[->, line width=1.5pt] (2.5,0) -- (3.5,0);
    \end{tikzpicture}
    \caption{Hexagonal hydrogen-bonded ice ring in flipped configurations}
    \label{fig:ice-ring}
\end{figure}

This is from him mostly verbatim:
Consider a mole of ice with $N$ molecules. 
The ice structure may form itself into a six-pointed ring with protons positioned along the sides
as in Figure \ref{fig:ice-ring}.
In the Bernal-Fowler scheme, a water molecule can orient itself in 6 different ways. 
However, there are only two unoccupied tetrahedral directions for each oxygen and the chance
that both can be aligned with the current orientation is $\frac{1}{4}$ hence the total number of 
configurations of a hexagonal water ring is 
\begin{equation}\label{eq:ice-ring-entropy}
    W = \left(\frac{6}{4}\right)^N = \left(\frac{3}{2}\right)^N \quad\implies\quad S = k\log\left[\frac{3}{2}\right]^N
\end{equation}

I might be able to provide some more evidence for this by reading a couple more papers.
Since the flexibility of the hydrogen bond network allows many different crystal arrangements, the
phase diagram (that is, the plot illustrating which arrangements are present at certain conditions)
is necessarily complex.
The important bit of the phase diagram is the part which is above 2 GPa.
The intersection between Ice--VII/--VIII is interesting because the transition takes place at essentially
a constant temperature over a considerable pressure increase.
The two phases are very similar, often reffered to as counterparts.
The main thing that's different between them is their proton ordering.
These phases of ice are pretty cool, for reasons that I'm sure I'll be able to explain.
I think it would be interesting to dive into how their properties are different simply by nature of their
symmetry properties.

\subsection{Molecular Dynamics}
Almost since computers became available to physicists, they have been trying to simulate the motion of
molecules on them.
With neutron scattering experiments being able to provide good data about the structure of crystals, MD
simulations give researchers a glimpse at how individual crystal consituents behave.
It may also be that simulating things is just a lot cheaper, I think this is a good motivator for people.
Alsom it may be that MD simulations are good for making predictions and setting up physical experiments. \\
The simplest MD models set up Newton's laws for the system, and solve for positions and velocities by integrating
numerically each timestep.
The forces experienced by individual molecules in this regime are represented by a `force field', which
is essentially the potential energy expression formed by the sum of all the different interactions.
Some interactions are weaker than others, and in particular some may be very time-consuming to compute,
and hence are neglected.
This is necessarily computationally intensive, but generally very accurate at describing the macroscopic 
properties. 
Molecules, however, exist in the 0.1 nanometer order of magnitude, and so implementing a classical approach
has certain drawbacks.
Monte-carlo MD simulations are also a thing and they have proved to be pretty good. 
I don't think that their particular function is very relevant but I think a brief overview for completeness
is a nice touch.
As computers have gotten better (I imagine?) and physical theories have improved (probably), \textit{ab initio}
MD simulations have become more popular.
These are simulations which solve for quantum effects explicitly each timestep using things like Density
Functional Theories (DFTs) rather than using Newton's laws.
I think it is important here to see when they first came about, because I think it is important if it turns out that
this has been a thing since the 70s.
\textit{Ab initio} is pretty computationally heavy though, and since each timestep is about 1 fs long and interesting
effects generally happen on the nanosecond ($10^6$ fs) to millisecond ($10^{12}$ fs) range, this creates some issues.
So people have come up with some pretty decent compromises.
These days, classical MD simulations are still the \textit{status quo} but with increasingly accurate `force field'
implementations with parameters determined by extenisve first-principles calculation. 
Certain water models have proven very popular.
TIP4P for example is pretty cool.
There is some room here to talk about certain algorithms whic hare important.
 
\subsection{AMOEBA Force Field}
What is the AMOEBA force field?
The simple answer is that it is a model which set out to model the electrodynamic interactions between molecules
more accurately.
Electrodynamics can have substantial impact on structure.
It is (one reason?) why the hydrogen bonding network takes the form it does.
To be more specific, the AMOEBA force field approached the problem from four directions: Atomic Multipoles, Polarization,
Induced Dipoles and Ewald Summation \cite{ren2003}. The final form that we get looks like 
\[ U = U_{\mathrm{bond}} + U_{\mathrm{angle}} + U_{\mathrm{b}\theta} + U_{\mathrm{oop}} + U_{\mathrm{torsion}}
+ U_{\mathrm{vdW}} + U^{\mathrm{perm}}_{\mathrm{ele}} + U^{\mathrm{ind}}_{\mathrm{ele}} \]
where (this is a quote here) the first five terms describe the short-range valence interactions (stretching, angle bending,
bond-angle cross term, out of plane bending, and torsional rotation) and the last three terms are the nonbonded vdW
and electrostatic contributions.
I think we don't have to worry about some of the first five, but definitely the last htree are important. 
It is $U^{\mathrm{ind}}_{\mathrm{ele}}$ which really sets this forcefield apart from a few others.
Here is some of the important math behind the development of the model:
\begin{description}
    \item[Atomic multipoles:]
        here is a short description with some math

    \item[Polarization:] 
        I expect there will be some more math here

    \item[Induced Dipoles:]
        some more stuff

    \item[Ewald summation:]
        some more stuff.
        be careful with this bit because I don't want to copy Ren and Ponders original paper.
        It is necessary to show some of the math though.
\end{description}
The AMOEBA model was initially developed as part of a water simulation thing. 
Its parameters were based on data from the liquid and gas-phases, although previous experiments have shown AMOEBA 
water to be decently accurate at reproducing the properties of low-pressure ice.
High-pressure ice is a different beast.
I'm not sure whether other models have shown reasonable success at these conditions or not but I'm sure that 
I could find out.
Although I believe that a source will corroborate this claim, electrostatic interactions become increasingly 
important for solid phases with increasing density.
The close-packed nature of the molecules mean that there are some pretty crazy electric files running around in there.
Definitely something to consider.
At this point I think I should discuss some other models of ice and see what we're working with.
